Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Italicize system names

\twocolumn[
\maketitle
\begin{onecolabstract}
  \begin{quote}\begin{quote}\begin{quote}
  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems that replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both \term{verifiable} and \term{secret}
	and analyze how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
	use cryptographic techniques to meet those goals.
	\end{quote}\end{quote}\end{quote}
  \vspace{1em}
\end{onecolabstract}
]

@@

In this survey, we study three of the most well-known solutions: the in-person voting systems
Scantegrity and \pv{} and the online voting system Helios.

@@

Another intuition which we will find useful in discussion of the Scantegrity II system is:
Assume a list of votes $a_1, a_1, \ldots, a_n$ is public, and the mapping between
voters and votes is described by a secret permutation $\pi_k$ such that the vote
belonging to voter $v_i$ is $a_{\pi_k(i)}$.
As long as an attacker cannot gain information about $\pi_k$,
the system reveals no more information than is implies by an anonymized list of votes.

@@

\section{Scantegrity}

The Scantegrity system \cite{scantegrity_ii} -- we consider an updated version technically known as
Scantegrity II -- is designed to provide verifiability atop existing in-person voting systems that
rely on fill-in ballots processed via optical scan.

@@

Before an election is held, the election authority must construct four Tables that lie at the core
of the Scantegrity system: Tables P, Q, R, and S (see Figure ~\ref{fig:scantegrity}).

@@

Table R comprises the heart of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of
these mappings is pseudorandom (though the mappings must obey the data specified in Table P for vote
correctness).

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{images/include/scantegrity.pdf}
	\caption{
		Visualization of links between Scantegrity tables.
		Lines represent pointers in Table R.
		Dashed lines represent secret (unpublished) values.
	}
	\label{fig:scantegrity}
\end{figure}

@@

A Scantegrity ballot consists of two portions: a special optical-scan ballot strip and a second
piece of paper that the voter will keep as a receipt. Each ballot is identified by a unique number,
which is printed on both portions. (While this number can be printed in plain sight, it can also be
encrypted on the optical-scan portion such that someone with physical access to a ballot box cannot
link a particular ballot to a voter with receipt in-hand.)

@@

\section{\pv{}}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{images/include/preta.pdf}
	\caption{\pv{} ballot}
	\label{fig:preta}
\end{figure}

@@

\section{Helios}

Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
system; however, it, too, is designed with an emphasis on verifiability.

@@

At the heart of Helios is a single ElGamal key pair. The secret key is known only to the Helios
server, but the public key can be accessed in some way by all participants.

@@

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
\term{mixnet}.

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
	\caption{Simple re-encryption \term{mixnet} like the one used in Helios}
	\label{fig:mixnet}
\end{figure}

@@

In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles,
referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
obtain the set of challenges allows this process to be completed entirely within the Helios system
-- without human involvement -- for publication and auditor verification.

Once auditors are satisfied with the proofs, Helios decrypts and tallies the ballots. Similarly,
Helios proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
decrypted ballots are in fact correct plaintexts for the corresponding mixnet outputs. Challenges
are generated by the system using a technique similar to that employed to provide mixnet proofs.

@@

In both Scantegrity and Helios, the following information is revealed after the election:
\begin{itemize}
	\item
		\emph{Some} information about \emph{all} encrypted ballots, linked to voters.
	\item
		\emph{All} decrypted ballots, \emph{not} linked to voters.
\end{itemize}

In Scantegrity, public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)

In Helios, the public ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, Helios uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about Helios's
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees. Scantegrity essentially has an immensely large
key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
decrypted. Helios, however, uses known algorithms with shorter keys that could potentially be
attacked. Compromise of keys in either system would destroy their privacy guarantees.

@@

Essentially, both Scantegrity and Helios use some mechanism to shuffle votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

In Scantegrity, the ballot mix is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R to votes in Table Q \emph{or} tallies in Table S be deterministic,
privacy would be compromised for half of all voters.

Where Table R lies between encryptions and decryptions in Scantegrity, Helios makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally.

At a high level, the difference between these two schemes is in the number of mappings that must be
kept secret in order to ensure ballot secrecy. In Scantegrity, Table R has one mapping to Table Q
and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
But in Helios, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
voters and tallies, respectively, without revealing the inner mapping. In some ways, Helios's
approach accomplishes the same goals as \emph{but} is implemented as an antithesis of Scantegrity's
Table system.

@@

At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that her
vote is recorded exactly as intended.

In Scantegrity, this verification is rolled into the ballot casting process. After recording the
receipt herself, a voter can visually check that the code on the receipt matches the candidates
selected on the ballot.

Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

While both systems provide the voter some assurance that the proper vote was recorded, Scantegrity's
verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
cast} was recorded properly.

@@

In the case on Scantegrity, this information is primarily embodied in the published version of Table
Q. After the election, a voter can compare her receipt code with that revealed for his ballot in
Table Q. If the code does not match, then something is amiss.

Helios, similarly, exposes a complete list of ballot hashes. A voter can examine this data set to
ensure that it accurately reflects the hash that was reported on screen when the ballot was cast.

@@

One source of vote auditing in Scantegrity relies on unused \term{audit ballots} to prove that its
Tables Q, R, and S accurately match ballot selections with the proper candidates. These ballots come
in two forms: a group of ballots randomly selected and checked prior to the election by members of
the election authority; and the collection of optional secondary ballots that are offered to voters.

@@

In some ways, Helios count verification is simpler than that in Scantegrity. We have already
discussed how Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
tallying is straightforward.

@@

Scantegrity prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
without exposure of the data maintained in Table P -- Scantegrity's secret -- the voter has no
way to prove to a third party that the claim is true.

An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
together \emph{are} Table P, and using special ink allows the codes to be printed without making it
easy for a ballot handler to simple read Table P from the ballots prior to the election.

Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus convincing the coercer
of something untrue.
This is one reason that it is important for the system to use a collision-resistant hash function.

@@

The creators of Helios note this fact, and it is reflected in their work, as the system makes at
least recording verification an obvious and easy process.

@@

In both Scantegrity and Helios, the most fundamental secret is a key. In Scantegrity, this is the
seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
ElGamal key pair used for all encryption/decryption operations during a particular election.

The random seed in Scantegrity is a secret that is shared among a group of members of the election
authority, thereby mitigating risk of compromise.

But in Helios, there is a single private ElGamal key that lives on the server. The
authors of Helios acknowledge this weakness but choose to overlook it, as they aim to make
verifiable voting an accessible technology, even with some costs.

Furthermore, with each of these systems, voters must \emph{still} place a significant level of trust
in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
we must place some trust in that party. In Scantegrity, for example, we must assume that we can
trust at least enough of the secret holders so that the seed cannot be obtained and used
inappropriately.

@@

It is clear that Scantegrity's secrets -- Tables P and R -- are generated using a source of true
randomness. If there is any determinism in generating those tables, an attacker could exploit the
generation method to violate privacy. Helios, on the other hand, was designed with application in
mind and therefore uses standard cryptographic techniques (ElGamal and SHA-1).

Given a flawless implementation of Scantegrity as specified in research, it can certainly provide the
security it claims. However, we note that an amateur implementation of the protocol laid out by
Scantegrity's creators -- e.g., one that uses a imperfect source of randomization -- could lead to a
very insecure system.

The same can be said for Helios, should it be implemented with inappropriate primitives (not ElGamal
and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
specification is less open to interpretation and, therefore, potentially harmful choices.

>>>>

\twocolumn[
\maketitle
\begin{onecolabstract}
  \begin{quote}\begin{quote}\begin{quote}
  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems that replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both \term{verifiable} and \term{secret}
	and analyze how three popular verifiable voting systems
	-- \term{Scantegrity}, \term{\pv{}}, and \term{Helios} --
	use cryptographic techniques to meet those goals.
	\end{quote}\end{quote}\end{quote}
  \vspace{1em}
\end{onecolabstract}
]

@@

In this survey, we study three of the most well-known solutions: the in-person voting systems
\term{Scantegrity} and \term{\pv{}} and the online voting system \term{Helios}.

@@

Another intuition which we will find useful in discussion of the \term{Scantegrity} system is:
Assume a list of votes $a_1, a_1, \ldots, a_n$ is public, and the mapping between
voters and votes is described by a secret permutation $\pi_k$ such that the vote
belonging to voter $v_i$ is $a_{\pi_k(i)}$.
As long as an attacker cannot gain information about $\pi_k$,
the system reveals no more information than is implies by an anonymized list of votes.

@@

\section{\term{Scantegrity}}

The \term{Scantegrity} system \cite{scantegrity_ii}
-- we consider an updated version technically known as \term{Scantegrity II} --
is designed to provide verifiability atop existing in-person voting systems that
rely on fill-in ballots processed via optical scan.

@@

Before an election is held, the election authority must construct four Tables that lie at the core
of the \term{Scantegrity} system: Tables P, Q, R, and S (see Figure ~\ref{fig:scantegrity}).

@@

Table R comprises the heart of the \term{Scantegrity} tables: it maps cast ballots in Table Q to tally marks
in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of
these mappings is pseudorandom (though the mappings must obey the data specified in Table P for vote
correctness).

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{images/include/scantegrity.pdf}
	\caption{
		Visualization of links between \term{Scantegrity} tables.
		Lines represent pointers in Table R.
		Dashed lines represent secret (unpublished) values.
	}
	\label{fig:scantegrity}
\end{figure}

@@

A \term{Scantegrity} ballot consists of two portions: a special optical-scan ballot strip and a second
piece of paper that the voter will keep as a receipt. Each ballot is identified by a unique number,
which is printed on both portions. (While this number can be printed in plain sight, it can also be
encrypted on the optical-scan portion such that someone with physical access to a ballot box cannot
link a particular ballot to a voter with receipt in-hand.)

@@

\section{\term{\pv{}}}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{images/include/preta.pdf}
	\caption{\term{\pv{}} ballot}
	\label{fig:preta}
\end{figure}

@@

\section{\term{Helios}}

\term{Helios} \cite{helios} -- unlike \term{Scantegrity} and \term{\pv{}} -- is an \emph{online} voting
system; however, it, too, is designed with an emphasis on verifiability.

@@

At the heart of \term{Helios} is a single ElGamal key pair. The secret key is known only to the \term{Helios}
server, but the public key can be accessed in some way by all participants.

@@

Once all ballots have been collected by the \term{Helios} server, they are shuffled by a cryptographic
\term{mixnet}.

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
	\caption{Simple re-encryption \term{mixnet} like the one used in \term{Helios}}
	\label{fig:mixnet}
\end{figure}

@@

In order to provide a guarantee of proper shuffling, \term{Helios} shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles,
referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that \term{Helios} must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
obtain the set of challenges allows this process to be completed entirely within the \term{Helios} system
-- without human involvement -- for publication and auditor verification.

Once auditors are satisfied with the proofs, \term{Helios} decrypts and tallies the ballots. Similarly,
\term{Helios} proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
decrypted ballots are in fact correct plaintexts for the corresponding mixnet outputs. Challenges
are generated by the system using a technique similar to that employed to provide mixnet proofs.

@@

In both \term{Scantegrity} and \term{Helios}, the following information is revealed after the election:
\begin{itemize}
	\item
		\emph{Some} information about \emph{all} encrypted ballots, linked to voters.
	\item
		\emph{All} decrypted ballots, \emph{not} linked to voters.
\end{itemize}

In \term{Scantegrity}, public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)

In \term{Helios}, the public ballot is a hash of an encryption. \term{Helios} uses ElGamal to encrypt ballots,
which -- unlike \term{Scantegrity}'s core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, \term{Helios} uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees. \term{Scantegrity} essentially has an immensely large
key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
decrypted. \term{Helios}, however, uses known algorithms with shorter keys that could potentially be
attacked. Compromise of keys in either system would destroy their privacy guarantees.

@@

Essentially, both \term{Scantegrity} and \term{Helios} use some mechanism to shuffle votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

In \term{Scantegrity}, the ballot mix is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R to votes in Table Q \emph{or} tallies in Table S be deterministic,
privacy would be compromised for half of all voters.

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{Helios} makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

At a high level, the difference between these two schemes is in the number of mappings that must be
kept secret in order to ensure ballot secrecy. In \term{Scantegrity}, Table R has one mapping to Table Q
and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
But in \term{Helios}, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
voters and tallies, respectively, without revealing the inner mapping. In some ways, \term{Helios}'s
approach accomplishes the same goals as \emph{but} is implemented as an antithesis of \term{Scantegrity}'s
Table system.

@@

At the time a ballot is cast, both \term{Scantegrity} and \term{Helios} attempt to ensure a voter that her
vote is recorded exactly as intended.

In \term{Scantegrity}, this verification is rolled into the ballot casting process. After recording the
receipt herself, a voter can visually check that the code on the receipt matches the candidates
selected on the ballot.

\term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

While both systems provide the voter some assurance that the proper vote was recorded, \term{Scantegrity}'s
verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
cast} was recorded properly.

@@

In the case on \term{Scantegrity}, this information is primarily embodied in the published version of Table
Q. After the election, a voter can compare her receipt code with that revealed for his ballot in
Table Q. If the code does not match, then something is amiss.

\term{Helios}, similarly, exposes a complete list of ballot hashes. A voter can examine this data set to
ensure that it accurately reflects the hash that was reported on screen when the ballot was cast.

@@

One source of vote auditing in \term{Scantegrity} relies on unused \term{audit ballots} to prove that its
Tables Q, R, and S accurately match ballot selections with the proper candidates. These ballots come
in two forms: a group of ballots randomly selected and checked prior to the election by members of
the election authority; and the collection of optional secondary ballots that are offered to voters.

@@

In some ways, \term{Helios} count verification is simpler than that in \term{Scantegrity}. We have already
discussed how \term{Helios} uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
tallying is straightforward.

@@

\term{Scantegrity} prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
without exposure of the data maintained in Table P -- \term{Scantegrity}'s secret -- the voter has no
way to prove to a third party that the claim is true.

An important point regarding \term{Scantegrity} is that it also relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
together \emph{are} Table P, and using special ink allows the codes to be printed without making it
easy for a ballot handler to simple read Table P from the ballots prior to the election.

\term{Helios}, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside: as with \term{Scantegrity}, \term{Helios} does not reveal to a voter all the
information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus convincing the coercer
of something untrue.
This is one reason that it is important for the system to use a collision-resistant hash function.

@@

The creators of \term{Helios} note this fact, and it is reflected in their work, as the system makes at
least recording verification an obvious and easy process.

@@

In both \term{Scantegrity} and \term{Helios}, the most fundamental secret is a key. In \term{Scantegrity}, this is the
seed to the pseudorandom number generator used to create Table P; and in \term{Helios}, it is a single
ElGamal key pair used for all encryption/decryption operations during a particular election.

The random seed in \term{Scantegrity} is a secret that is shared among a group of members of the election
authority, thereby mitigating risk of compromise.

But in \term{Helios}, there is a single private ElGamal key that lives on the server. The
authors of \term{Helios} acknowledge this weakness but choose to overlook it, as they aim to make
verifiable voting an accessible technology, even with some costs.

Furthermore, with each of these systems, voters must \emph{still} place a significant level of trust
in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
we must place some trust in that party. In \term{Scantegrity}, for example, we must assume that we can
trust at least enough of the secret holders so that the seed cannot be obtained and used
inappropriately.

@@

It is clear that \term{Scantegrity}'s secrets -- Tables P and R -- are generated using a source of true
randomness. If there is any determinism in generating those tables, an attacker could exploit the
generation method to violate privacy. \term{Helios}, on the other hand, was designed with application in
mind and therefore uses standard cryptographic techniques (ElGamal and SHA-1).

Given a flawless implementation of \term{Scantegrity} as specified in research, it can certainly provide the
security it claims. However, we note that an amateur implementation of the protocol laid out by
\term{Scantegrity}'s creators -- e.g., one that uses a imperfect source of randomization -- could lead to a
very insecure system.

The same can be said for \term{Helios}, should it be implemented with inappropriate primitives (not ElGamal
and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
specification is less open to interpretation and, therefore, potentially harmful choices.
